Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-08-30 referee_responses.tex

\textsf{AR: Changed to "In CLM4 projections, the inclusion of N dynamics significantly limits the ability of the terrestrial biosphere to ... "}

- Line 52-3: Is that true? Unless that can be supported I would suggest omitting. 
\textsf{AR: We have deleted this section,}

- Line 64: It would be good not to overlook the numerous earlier studies that did actually explore these issues ... e.g. Rastetter et al. (1991) Tree Physiology 9, 101 -126.; Comins \& McMurtrie (1993) Ecological Applications 3, 666-681.; Kirscbaum et al. (1994) Plant, Cell \& Environment, 17: 1081-1099, etc.

\textsf{AR: Thanks for the references. I didn't know about those. We've deleted that section as a way to reframe the introduction to be more general and less focused on the N modifications.}

@@

AR: \textsf{We have reduced the amount of text devoted to this idea.}

Results 
-------

- Line 423: To not look at soil outputs feels like an oversight to me. At the very least, linking the results to available plant N in the soil would be very interesting. Many of the changes have feedbacks for the soil and I think it is important to consider the responses of some of these variables too.

\textsf{AR: Thanks for the suggestion. We added the N fixation rates and the soil N content to the plots and the discussion.s}

@@

L829: replace "(/citewieder2019" with proper text.

\textsf{AR: Done.}

Table 1: What's default? Also, why some scenarios have the same multipliers?

\textsf{AR: The defaults are complex to illustrate, as some vary by PFT, others do not, etc. We have now removed the duplicate range parameters, which were set as such on account of limited constraints of their ranges. }
